---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(regulationsgov)

```


# regulationsgov

<!-- badges: start -->
[![R-CMD-check](https://github.com/q-w-a/regulationsgov/workflows/R-CMD-check/badge.svg)](https://github.com/q-w-a/regulationsgov/actions)
<!-- badges: end -->

The package regulationsgov is designed to enable users to access and engage with textual data from the [Regulations.gov API](https://open.gsa.gov/api/regulationsgov/). 

## Installation

You can install the development version of regulationsgov from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
remotes::install_github("q-w-a/regulationsgov")
```

## First Steps

To access the [Regulations.gov API](https://open.gsa.gov/api/regulationsgov/), you will need to obtain an API key [here](https://open.gsa.gov/api/regulationsgov/#getting-started). 

Once you have this key, you can provide it to every time you call one of the functions requiring authentication using the `key` argument, but it may be easiest to set it up as an environmental variable. You can do this with the following function.

```{r, eval = FALSE}

library(regulationsgov)

set_datagov_key("PUT_KEY_HERE")


```


If you run `set_datagov_key`, you don't need to provide the key as an argument to functions in this package. You only need to run it once. However, if you choose to not set it up, you can just provide the key to the functions requiring authentication.


### Example: Retrieving Comments for a Specific Docket 

For example, here we retrieve all comment metadata, including the download links, for the docket [CMS-2014-0063](https://www.regulations.gov/docket/CMS-2014-0063). First, we do so assuming we have set up the key.


```{r, eval = FALSE}

# retrieve all comments for the docket CMS-2014-0063
comments_CMS_2014_0063 <- get_all_comments(docketId = "CMS-2014-0063")

```

If the key is not set up, then we provide the key with the `key` argument. Here, you need to replace `DEMO_KEY` with your specific key unless you are running a very limited number of calls (the rate limit for `DEMO_KEY` is much lower than an ordinary API key).

```{r, eval = FALSE}


# retrieve all comments for the docket CMS-2014-0063
comments_CMS_2014_0063 <- get_all_comments(docketId = "CMS-2014-0063", key = "DEMO_KEY")


```


After running this command, if needed you can access it as an environmental variable with

```{r, eval = FALSE}

Sys.getenv("DATA_GOV_KEY")

```

but this will likely be unnecessary for use of the functions in this package.


### Example: Retrieving the Documents Associated with a Specific Docket 

Here, we obtain document and metadata for all documents associated with the docket [FDA-2009-N-0501](https://www.regulations.gov/docket/FDA-2009-N-0501). 


```{r, message = FALSE}

library(dplyr)

documents <- regulationsgov::get_all_documents(docketId ="FDA-2009-N-0501")


glimpse(documents)

```


### Example: Retrieving the Comments Associated with a Specific Docket

In this case, there are only 13 comments associated with docket `FDA-2009-N-0501`. We can obtain them with the function
`get_all_comments`. You might notice the same individual has submitted multiple comments, which we also can verify [here](https://www.regulations.gov/docket/FDA-2009-N-0501/comments).

```{r}

comments <- regulationsgov::get_all_comments(docketId ="FDA-2009-N-0501")

comments %>%
  select(data_id, 
         data_title,
         data_stateProvinceRegion) %>%
  glimpse()

```


Of particular interest may be the `fileUrl` column, which allows us to download the text.

For example, to download any attachments for the comments and place them in the directory `comments_FDA_2009_N_0501`, we can run

```{r, eval = FALSE}

download_all(data_frame = comments, 
             dest = "../comments_FDA_2009_N_0501", 
             quiet = TRUE)

```

and to download the documents themselves to the directory `docs_FDA_2009_N_0501` we can run the following.

```{r, eval = FALSE}

download_all(data_frame = documents, 
             dest = "../docs_FDA_2009_N_0501", 
             quiet = TRUE)


```

